EGALITARIAN ASPECTS OF SCALE-FREE NETWORKS

### 2017-08-19 article/article.tex
arrumada questao do formalismo institucional e retirada primeira sentenca da intro

\begin{abstract}
Scale-free networks are frequently described as the zenith of inequality and sometimes even pin-pointed
	as a natural cause of concentrations, including accumulation of resources in human society.
Although coherent with theory and empirical data,
	there are at least three aspects of scale-free networks that are egalitarian.
	Using the social network metaphor (which is easier to grasp):
	1) the presence of each agent (vertex or component) in diverse networks,
	while each agent has the same amount of resources (e.g. time) for engaging (establishing links or edges) with other individual agents,
	ideas or objects;
	2) the constant change in the concentration of resources (in this case, links) of each agent;
	3) the uniform distribution of resources with respect to the amount of resources per agent (the more resources per agent, the fewer the agents).
We also consider an antithesis: the formalism of institutionalized roles might impose both a less dynamic variation of participant roles,
and a less extreme concentration of resources.
The conclusions suggest the urge of research to better examine and model the importance of the vertices
	that are not hubs (i.e. peripheral and intermediary) and
	verify the need to better weight the emphasis current literature
places in the association of inequality to the scale-free networks (and other phenomena in which power laws are found).
\end{abstract}

@@

\pagestyle{fancy}                                   j

\section{INTRODUCTION}
The history of the concept of scale-free networks includes controversies and resulting disagreements.
\cite{price1}
reported that citations networks had a heavy-tailed distribution following a power law.
He also described a ``cumulative advantage'' that explains the power law~\citep{price2}.
This same networks with a power-law distribution of connectivity is nowadays called ``scale-free''
and the same explanation for the distribution is called ``preferential attachment'',
as the result of a rediscovery of the property by~\cite{barabasi1}.
This power-law rediscovery, and the rediscovery of small-world networks by~\cite{small},
is usually considered the birth of the complex networks field,
in the turn of the millennium.
In the last decade and a half,
most of the articles in physics report advances in complex networks.

@@

@@

Further work should involve attempts to answer the questions and follow the recommendations above,
further confirm or refute the arguments in this documents, and:
\begin{itemize}
	\item develop models to reflect the fundamental roles performed by nodes beyond hubs (i.e.
		peripherals and intermediary).
	\item Deepen the model exposed in~\cite{fabbri3} and submit it to peer review processes in order
		to understand the extent of its validity.
	\item Study the dynamics of individual agents in social networks with respect to the concentration of links,
		as suggested in~\cite{fabbri1,fabbri2,versinus}.
	\item Study the integration of the networks, maybe by using the database in~\cite{losd} which
		contains a number of networks with shared participants.
	\item Deepen the absorption of the literature and the partnership with academics which produce
		knowledge within the complex networks field, both to better understand the convictions
		and to spread our concerns.
\end{itemize}
% Are there other egalitarian aspects which we are not taking into account?

>>>>

\begin{abstract}
Scale-free networks are frequently described as the zenith of inequality and sometimes even pin-pointed
	as a natural cause of concentrations, including accumulation of resources in human society.
Although coherent with theory and empirical data,
	there are at least three aspects of scale-free networks that are egalitarian.
	Using the social network metaphor (which is easier to grasp):
	1) the presence of each agent (vertex or component) in diverse networks,
	while each agent has the same amount of resources (e.g. time) for engaging (establishing links or edges) with other individual agents,
	ideas or objects;
	2) the constant change in the concentration of resources (in this case, links) of each agent;
	3) the uniform distribution of resources with respect to the amount of resources per agent (the more resources per agent, the fewer the agents).
	We also consider the importance of vertices that are not hubs and overstatements on the importance of the hubs.
The conclusions suggest the urge of research to better examine and model the importance of the vertices
	that are not hubs (i.e. peripheral and intermediary) and
	verify the need to better weight the emphasis current literature
places in the association of inequality to the scale-free networks (and other phenomena in which power laws are found).
\end{abstract}

@@

\pagestyle{fancy}

\section{INTRODUCTION}
\cite{price1}
reported that citations networks had a heavy-tailed distribution following a power law.
He also described a ``cumulative advantage'' that explains the power law~\citep{price2}.
This same networks with a power-law distribution of connectivity is nowadays called ``scale-free''
and the same explanation for the distribution is called ``preferential attachment'',
as the result of a rediscovery of the property by~\cite{barabasi1}.
This power-law rediscovery, and the rediscovery of small-world networks by~\cite{small},
is usually considered the birth of the complex networks field,
in the turn of the millennium.
In the last decade and a half,
most of the articles in physics report advances in complex networks.

@@

\section{ANTITHESIS}\label{sec:anti}

@@

Further work should involve attempts to answer the questions and follow the recommendations above,
further confirm or refute the arguments in this documents, and:
\begin{itemize}
	\item develop models to reflect the fundamental roles performed by nodes beyond hubs (i.e.
		peripherals and intermediary).
	\item Deepen the model exposed in~\cite{fabbri3} and submit it to peer review processes in order
		to understand the extent of its validity.
	\item Study the dynamics of individual agents in social networks with respect to the concentration of links,
		as suggested in~\cite{fabbri1,fabbri2,versinus}.
	\item Study the integration of the networks, maybe by using the database in~\cite{losd} which
		contains a number of networks with shared participants.
	\item Deepen the absorption of the literature and the partnership with academics which produce
		knowledge within the complex networks field, both to better understand the convictions
		and to spread our concerns.
	\item Consider an antithesis: the formalism of institutionalized roles
		might impose both a less dynamic variation of participant roles,
		and a less extreme concentration of resources.
\end{itemize}
% Are there other egalitarian aspects which we are not taking into account?
